Still Missing a Cool Title

### 2006-05-31 talk/dls2006/paper.tex
use lattice{1,2}.pdf.  about zero thought went in to the amount of scaling to use and the captions; tweaking may be desirable.

\item $NullableStr$, $NullableInst(class)$ -- a string or
      \texttt{None}; resp. an instance or \texttt{None}.
\end{itemize}
%
Figures 6 and 7 shows how these types are ordered to form a lattice.  We
mostly use its structure of [join-semilattice] only.

\begin{verbatim}
.. graphviz:: image/lattice1.dot

:Figure 6: the lattice of annotations.
\end{verbatim}

\begin{verbatim}
.. graphviz:: image/lattice2.dot

:Figure 7: The part about instances and nullable instances, assuming a
           simple class hierarchy with only two direct subclasses of
           \texttt{object}.
\end{verbatim}

>>>>

\item $NullableStr$, $NullableInst(class)$ -- a string or
      \texttt{None}; resp. an instance or \texttt{None}.
\end{itemize}
%
Figures \ref{latticeoverall} and \ref{latticedetail} show how these
types are ordered to form a lattice.  We mostly use its structure of
[join-semilattice] only.

\begin{figure*}
\centering
\includegraphics[scale=0.75]{image/lattice1.pdf}
\caption{The overall lattice}
\label{latticeoverall}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.75]{image/lattice2.pdf}
\caption{The part about instances and nullable instances, assuming a
  simple class hierarchy with only two direct subclasses of
  \texttt{object}.}
\label{latticedetail}
\end{figure*}
